Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-06 paper/main.tex
Updates

We use a slightly modified version of Pillai's Trace for our purpose for two
main reasons: 1) It uses all the canonical correlation values, capturing the
full extent of association, 2) Its interpretation is similar to Pearson's
correlation coefficient, i.e., $ 0 $ signifies no association and $ 1 $
signifies perfect linear relationship. This leads to our proposed measure of
conditional association: We divide to make the measure normalized when comparing
between pair of variables with different number of categories.

@@

>>>>

We use a normalized version of Pillai's Trace for our purpose, given as:

@@

We use Pillai's Trace because: 1) It uses all the canonical correlation values,
capturing the full extent of association, 2) Its interpretation is similar to
Pearson's correlation coefficient, i.e., $ 0 $ signifies no association and $ 1
$ signifies perfect linear relationship. We use a normalized version because
when comparing between pair of variables with different number of categories.
